### 2021-08-19 README.Rmd
Added option of using text as saunames in controlfile. No EWN

* 2021-08-12 aMSE 0.0.0.500 Modified do_MSE and added plothsstats, streamlined the conditioning. No EWN.

* 2021-08-02 aMSE 0.0.0.700 Revised the 'ctrlfiletemplate' and 'datafiletemplate' functions to reflect the new usage. It should now be possible to run an example scenario related to M15h75.

@@

```{r example, echo=TRUE}
# a constant TAC example
starttime <- (Sys.time())
options("show.signif.stars"=FALSE,
        "stringsAsFactors"=FALSE,
        "max.print"=50000,
        "width"=240)
# declare libraries ------------------------------------------------------------
library(aMSE)
library(rutilsMH)
library(makehtml)
library(knitr)
# Obviously you should modify the rundir and datadir to suit your own setup
prefixdir <- "C:/A_Mal/scenarios/"
verbose <- TRUE
postfixdir <- "M15h75"
rundir <- paste0(prefixdir,postfixdir)
datadir <- rundir
alldirExists(rundir,datadir,verbose=verbose)
controlfile <- "controlM15h75.csv"
# equilibrium zone -------------------------------------------------------------
# You now need to ensure that there is, at least, a control.csv, and a 
# constantsdata.csv file in the data directory plus some other data .csv files
# depending on how conditioned you want the model to be. Templates for the
# correct format can be produced using ctrlfiletemplate(), datafiletemplate().
# 
# Of course, usually one would use data files, control.csv and a saudata.csv, which
# is listed as the datafile within the control.csv. These must be stored in 
# rundir. There are example files in the DropBox folder:
# .\..\Dropbox\National abalone MSE\aMSE_files\scenarios\examplerun. Read the 
# 'Using_aMSE' section in the Documentation .docx file in the documentation 
# directry  Then, assuming you have the very latest version of aMSE = 500, 
# the code in the documentation file (or in the 'run_aMSE.R' file within the
# examplerun subdirectory should work.

>>>>

* 2021-08-19 aMSE 0.0.0.400 Can now have text as SAU names in the Control file, this will use those names to label all plots (still working on tbles and extra polishing),

* 2021-08-13   aMSE 0.0.0.500 removed NumNe (midyear numbers-at-size) and introduced cutcatchN as an argument to do_MSE, which removes all size class data from teh catchN array with size-classes less than cutcatchN, whose default = 56 (2 - 110mm removed). This saves a good deal of space.

@@

```{r example, echo=TRUE}
# a constant TAC example
starttime <- (Sys.time())
options("show.signif.stars"=FALSE,
        "stringsAsFactors"=FALSE,
        "max.print"=50000,
        "width"=240)
# declare libraries ------------------------------------------------------------
library(aMSE)
library(rutilsMH)
library(makehtml)
library(knitr)
# Obviously you should modify the rundir and datadir to suit your own setup
prefixdir <- "C:/A_Mal/aa_scenarios/"
verbose <- TRUE
postfixdir <- "M15h75"
rundir <- paste0(prefixdir,postfixdir)
datadir <- rundir
alldirExists(rundir,datadir,verbose=verbose)
controlfile <- "controlM15h75.csv"
# equilibrium zone -------------------------------------------------------------
# You now need to ensure that there is, at least, a control.csv, and a 
# constantsdata.csv file in the data directory plus some other data .csv files
# depending on how conditioned you want the model to be. Templates for the
# correct format can be produced using ctrlfiletemplate(), datafiletemplate().
# 
# Of course, usually one would use data files, control.csv and a saudata.csv, which
# is listed as the datafile within the control.csv. These must be stored in 
# rundir. There are example files in the DropBox folder:
# .\..\Dropbox\National abalone MSE\aMSE_files\scenarios\examplerun. Read the 
# 'Using_aMSE' section in the Documentation .docx file in the documentation 
# directry  Then, assuming you have the very latest version of aMSE = 500, 
# the code in the documentation file (or in the 'run_aMSE.R' file within the
# examplerun subdirectory should work.
